A higher order approximate static condensation method for multi-material diffusion problems

### 2019-06-10 answer_to_reviewers.tex

%\include{commands.tex}

\usepackage{dutchcal}
\newcommand{\vect}[1]{\boldsymbol{\mathbf{#1}}}
\newcommand{\mfaces}[1][]{{\vect{\mathcal f}_{\text{#1}}}}
\newcommand{\bfaces}[1][]{{\vect{\mathcal F}_{\text{#1}}}}

%\pagestyle{empty}
\begin{document}

\begin{center}A list of changes  and responses to reviewers for ``A higher order approximate static condensation method for multi-material diffusion problems'' by A. Zhiliakov, D. Svyatskiy, M. Olshanskii, E. Kikinzon, M. Shashkov.
\end{center}
\bigskip

%We are grateful to the reviewers for a careful read of the manuscript and constructive suggestions, which lead to an improved paper.
%We addressed all points raised by the reviewers as outlined below.  \\

@@

%\centerline{
%{\Large {SISC manuscript \#M116618}}
%}

Reviewer 1 requested no modifications to the manuscript. Thus, in this document we are  addressing the points raised by Reviewer 2.

\textbf{Answers to Reviewer 2}

The authors would like to thank the Reviewer for a careful read of the manuscript and his/her comments and
constructive suggestions, which led to an improved paper. We addressed all points raised by the reviewers as outlined below.
In the following
we use italic font to quote the Reviewer.
Our revised article has been modified accordingly, with the changes {highlighted in blue}.\\

@@

\emph{(3) Page 6, right above equation (7): ``we need to distinct the vector" should be changed to ``we need to distinguish the vector"}

Fixed.

\emph{(4) Page 7: ``However, we cannot do this in a straightforward way, since the discontinuity of material interfaces across the macro-mesh faces may lead to a mismatch of discrete fluxes... including different space dimensions." This sentence can be written more clearly. In particular, the phrase ``including different space dimensions" is a bit confusing. I think you are alluding to the fact that neighboring macro cells $T^{+}$ and $T^{-}$ that share a macro-face in $\bfaces_{\text{int}}$ can have different numbers of (mini) faces that make up the macro-face (i.e., $\#\mfaces[ext](T^+) \neq \#\mfaces[ext](T^-)$), and therefore the concentration vectors~$\vect \lambda_{\boldsymbol{\tau}}$, restricted to each macro-face, can be of different sizes (and, even if the sizes are the same, the location of the faces will be different and so matching these values is not trivial). You might want to put in a sentence or two spelling this out more, and perhaps point to Figure 2 in the description. Introducing the phrase ``micro-face" and the notation $\mfaces[ext](T^+)$, etc., earlier, as done on page 7, will help with the clarity.}

We elaborated on this (page 7, paragraph 3) and added Figure 3 to illustrate the d.o.f. mismatch.

@@

We made the definition of~$\vect C_{\boldsymbol{\tau}}$ more precise (page 6, below equation (6)). We also added equation~(18) on page 9 where we precisely defined ``signed distances" to make the flux continuity condition written in the matrix form more transparent. Hence ``equation (18) is the equation (19) written in matrix form" now reads as ``equation (19) is the equation (20) written in matrix form."

We simplified the second continuity condition in (19), page 10, by integrating the first moment~$s_1$. This makes it easy to see the matrix form in the equation~(20).

\emph{(8) Page 11: ``Clearly, matrix $\mathbf{R}_{\boldsymbol{\tau}}$ has a non-trivial kernel iff $s_{ki}=s_{kj}, \quad i,j=1,\ldots,m_{k}$. Shouldn't it be: iff there is a $k$ such that $s_{ki}=s_{kj}$ for some $i$ and $j$? For example, $\mathbf{R}_{\boldsymbol{\tau}}$ just below equation (17) shares two rows and so is singular if, e.g., $s_{21}=s_{22}$.}

%After the previous correction, ``$\mathbf{R}_{\boldsymbol{\tau}}$ just below equation (17) shares two rows and so is singular if, e.g., $s_{21}=s_{22}$" reads as ``$\mathbf{R}_{\boldsymbol{\tau}}$ just below equation (18) shares two rows and so is singular if, e.g., $s_{21}=s_{22}$."

Matrix~$\mathbf{R}_{\boldsymbol{\tau}}$ is not singular for it is not a square matrix if the corresponding cell has a multi-material face. We only prove that it has a trivial kernel, i.e. its columns are linearly independent, which is indeed the case if $s_{ki}\neq s_{kj}$ for some $i\neq j$. So no changes are needed here.

\emph{(9) ``It is important to take into accont", page 15, accont $=>$ account"}

%
%\textbf{Other minor changes}
%
%The changes are \hl{highlighted in yellow}.
%
%(1) Page 2, paragraph 2: ``standard discretization thechniques" changed to ``standard discretization techniques."

### 2019-06-10 asc.tex
Add Maxim's iteration

\title{A higher order approximate static condensation method for multi-material diffusion problems}
\author{
	Alexander Zhiliakov\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (alex@math.uh.edu).}
	\and Daniil Svyatskiy\thanks{Los Alamos National Laboratory, Los Alamos,
		New Mexico, USA (dasvyat@lanl.gov).}
	\and
	Maxim Olshanskii\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (molshan@math.uh.edu); Partially supported by NSF through grant  DMS-1717516.}
	\and Evgeny Kikinzon \thanks{Los Alamos National Laboratory, Los Alamos,
		New Mexico, USA (kikinzon@lanl.gov).}
	\and Mikhail Shashkov\thanks{Los Alamos National Laboratory, Los Alamos,
		New Mexico, USA (shashkov@lanl.gov).}
}

@@

	Past decades evidenced an explosive \hlcyan{growth in the development of efficient computational techniques} for problems with evolving interfaces, which involve interaction between many materials or different phases of matter. These developments include immersed boundary method~\cite{peskin2002immersed}, immersed interface method~\cite{leveque1994immersed}, and unfitted finite element methods \cite{belytschko2009review,burman2015cutfem}, to name several popular numerical approaches. Depending on how the interface is treated numerically, one can distinguish between methods that smear the interface over a strip of finite thickness which should be further resolved by the mesh, like in the phase field approach~\cite{steinbach2009phase}, and methods that use a sharp interface representation, as in the level-set method \cite{sethian1999level}.  If one applies a sharp representation to handle complex geometries or interfaces undergoing large deformations, it is convenient to allow the  interface to cut through the background mesh in an arbitrary way. In turn, this leads to the problem of building accurate and stable approximations for  so-called multi-material cells, i.e. the mesh cells intersected by material interfaces. In particular, one is interested in discretizations which are robust with respect to how interfaces intersect the mesh and with respect to the contrast of  material properties, e.g. the ratio of physical parameters. This is the setting and the problem  we focus in this paper.

@@

One standard approach to handle  multi-material cells is a homogenization procedure. In this approach, one assigns to the cells  artificial homogeneous  material properties, which are calculated based on the volumetric shares of different materials in each of the multi-material cells. This enables one to apply standard discretization \hl{techniques}. %if one needs to solve for other physics, such as the heat transfer, on every time step of the simulation.
     %Then, ad-hoc methods can be used to interpolate the solution for the contained materials based on
Further one recovers solution in each phase from the computed cell-averaged values~\cite{dawes2013solving}.
Although being technologically straightforward, the homogenization approach often fails  to accurately model subcell material interactions, which results in non-physical numerical solutions to problems with high-contrast material properties.

@@

	Denote by $\bfaces$ the collection of all faces of the macro-mesh $\bmesh$. \hlcyan{We shall distinguish between the subset of internal and external faces},  $\bfaces = \bfaces[int] \cup \bfaces[ext]$\footnote{For the sake of  notation, we shall use~$\bfaces$ to denote both the set of elements and the corresponding domain formed by their union~$\cup_{F\in \bfaces} \bar{F}$; same for $\bfaces[int]$, $\bfaces[ext]$ and other collections of mesh elements introduced later in the text. The meaning should be clear from a context.}.
	Introducing the new unknown $\lambda \in \HHalfSpace[\bfaces]$, we reformulate \eqref{dual}--\eqref{dual:bc} as a system of local problems coupled through the boundary data
	and flux continuity condition:
	\begin{eqnarray}
		\arraycolsep=2pt\def\arraystretch{1.5}
		\left\{\begin{array}{rcrccl}
			\vect K^{-1}\,\vect u                    & + & \nabla\,p & = & 0       &\quad\text{in } \bcell, \\
			\nabla\cdot\vect u                       & + & c\,p      & = & f       &\quad\text{in } \bcell, \\
			                                         &   & p         & = & \lambda &\quad\text{on } \partial\bcell, %\label{dual_mini:trace}
		\end{array}\right.
		& \qquad \forall~\bcell\in\bmesh, \label{dual_mini} \\
		\llbracket\vect u \cdot \hat{\vect n}\rrbracket = 0\quad\:\:\text{on } F,\:\:\:\:
		& \qquad\quad \forall~F\in\bfaces[int]. \label{flux_cond}
	\end{eqnarray}
	Here $\hat{\vect n}$ denotes a normal vector to the face $F\in\bfaces[int]$ and $\llbracket \vect u\cdot\hat{\vect n} \rrbracket$ is the jump of the normal flux across $F$. On the outer boundary $\partial\Omega$ we assume \eqref{dual:bc}.

@@

	Consider an arbitrary but fixed cell $T\in\bmesh$. We now introduce the discretization of the local diffusion problem \eqref{dual_mini} in $T$. To this end, we consider the local mesh $\mmesh(T)$ of $T$, which is referred as mini-mesh. While the original triangulation $\bmesh$ is referred as macro-mesh.
	\begin{wrapfigure}{r}{0.4\textwidth}
		\vspace{-10pt}
		\begin{center}
			\includegraphics[width=0.3\textwidth]{./ring_mini_voronoi_cell.png}%{./Pictures/mainscreen1.png}
			\caption{Local polyhedral mesh for a three-material cell $T\in\bmesh$ \label{fig:mmesh}}
		\end{center}
		\vspace{-15pt}
		\vspace{1pt}
	\end{wrapfigure}
	If $T$ contains only one phase or material, then we obviously have $\mmesh(T) = \{\bcell\}$. Otherwise for the cell shared by several phases, $\mmesh(T)$ consists of polygonal elements, forming a tessellation of $T$, such that any ${\tau \in \mmesh(T)}$ contains only one phase/material; see Figure~\ref{fig:mmesh}. We denote by $\mfaces(T)$ the set of all faces in $\mmesh(T)$, which collects both   internal and boundary (external) faces with respect to $T$,  $\mfaces(T) = \mfaces[int](T) \cup \mfaces[ext](T)$. \hlcyan{If the meaning is not clear from the context, we will refer to elements of~$\mfaces(T)$ as ``mini-faces," and to elements of~$\bfaces$ as ``macro-faces."} Thus for the example of local mesh drafted in Figure~\ref{fig:mmesh}, we have three elements in $\mmesh(T)$, two internal faces from $\mfaces[int](T)$ and eleven external faces from $\mfaces[ext](T)$. It is clear that this local mesh is fitted to the material interfaces.

@@

	Given the above definition of the degrees of freedom on the local mesh we apply the mimetic finite difference (MFD) method from~\cite{lipnikov2014mimetic}. The method leads to the following system of equations with the matrix having the block structure:
	\begin{equation}\label{local}
		\begin{pmatrix}
			\phantom{-}\vect M_\mmesh & \vect B^T_\mmesh \\
			-\vect B_\mmesh & \vect \Sigma_\mmesh
		\end{pmatrix}
		\begin{pmatrix}
			{\vect u}_\mmesh \\
			{\vect p}_\mmesh
		\end{pmatrix}
		=
		\begin{pmatrix}
			\vect E_\mmesh\,\vect C_\mmesh\,{\vect \lambda}_\mmesh \\
			{\vect f}_\mmesh
		\end{pmatrix}.
	\end{equation}
	Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively; \hlcyan{$-\vect C_\mmesh$ is a diagonal scaling matrix that has mini-faces' measures~$|f|$ on the diagonal, $f \in \mfaces[ext](T)$, i.e. the mass matrix for ${\vect \lambda}_\mmesh$ unknowns};
	$\vect E_\mmesh \in \mathbb{R}^{n_f \times n_\lambda}$ is a rectangular matrix with 0 and 1 entries which sparsifies a vector from  $\mathbb{R}^{n_{\lambda}}$
	to a vector from  $\mathbb{R}^{n_{f}}$.
	For the details on MFD and accurate definition of the matrices we refer to \cite{lipnikov2014mimetic,MFDbook}.
	Here we need the property that  $\vect B_\mmesh$ has a full row rank, and $\vect M_\mmesh = \vect M^T_\mmesh$ is positive definite.

	Since the continuity of flux condition \eqref{flux_cond} and boundary conditions are enforced on  the \emph{external} edges of $T$, \hlcyan{we need to distinguish the vector} ${\vect u}^\text{ext}_\mmesh$ of fluxes on $\mfaces[ext](T)$, which is just a trivial restriction of ${\vect u}_\mmesh$ on the edges  from $\mfaces[ext](T)$,
	\begin{equation}\label{system_mini}
		{\vect u}^\text{ext}_\mmesh \coloneqq \vect E_\mmesh^T\,{\vect u}_\mmesh,
	\end{equation}
	where $\vect E_\mmesh^T$ is the restriction matrix with entries equal $0$ or $1$.

@@

	Next, we should use the continuity of flux condition \eqref{flux_cond} and boundary conditions to obtain a complete system for ${\vect u}^\text{ext}_\mmesh$ and ${\vect \lambda}_\mmesh$. However, we cannot do this in a straightforward way, since the discontinuity of material interfaces across the macro-mesh faces may lead to a mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$. \hlcyan{We elaborate on this below.}

	\hlcyan{For $F \in \bfaces[int]$ shared by two polygonal cells~$\bcell^\pm\in \bmesh$ denote by~$\mfaces_F(T^\pm) \subset \mfaces_{\text{ext}}(T^\pm)$ the subsets of mini-faces that belong to the macro-face~$F$ from each side. In general, $\mfaces_F(T^+)$ and $\mfaces_F(T^-)$ can have different numbers of mini-faces that make up the macro-face~$F$, i.e. $\#\,\mfaces_F(T^+) \ne \#\,\mfaces_F(T^+)$, and hence the restrictions of concentration vectors~${\vect \lambda}_\mmesh$ and fluxes vectors~${\vect u}^\text{ext}_\mmesh$ can be of different sizes. Moreover, even if~$\#\,\mfaces_F(T^+) = \#\,\mfaces_F(T^+)$, locations of the mini-faces may be different due to volume- or moment-of-fluid interface reconstruction. See an example on Figure~{\ref{fig:mismatch}}.}

	\begin{figure}[h]
		\begin{subfigure}{.49\linewidth}
			\svginputw{e_plus_e_minus.pdf_tex}
		\end{subfigure}%
		\quad
		\begin{subfigure}{.49\linewidth}
			\hlcyan{We have $3 = \#\,\mfaces_F(T^+) \ne \#\,\mfaces_F(T^+) = 2$. Note also that locations of mini-faces corresponding to the same material are different from each side of~$F$}
		\end{subfigure}
		\caption{\hlcyan{Example of the mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$}}
		\label{fig:mismatch}
	\end{figure}

	\hlcyan{This makes matching concentration and fluxes values not trivial.} Therefore, we shall enforce the flux continuity condition in the spirit of the mortar finite element method~\cite{mortar} using the space of functions defined on $\bfaces[int]$, which are polynomials of degree at most $n$ on every $F\in\bfaces[int]$, an analog of the Lagrange multiplier space in the mortar method:
	\[
		\Lambda=\left\{\lambda\in \LTwoSpace[{\bfaces[int]}]\,:\, \lambda\in P_n~\text{for any}~F\in\bfaces[int]\right\}.
	\]

	When the Lagrange multiplier space $\Lambda$ couples local MFD solutions, it is convenient to define
	degrees of freedom for $\lambda\in\Lambda$ in terms of its~$(n+1)$ moments $\lambda^{(i)}_F$ on every internal face $F\in\bfaces[int]$:
	\begin{equation}\label{asc_dofs}
		\lambda^{(i)}_F=\frac{\int_F  \lambda\,s_i \diff l}{|F|}, \quad i = 0, \dots, n.
	\end{equation}
	Here~$\{\,s_i\,\}_{i=0,\dots,n}$ is the set of \hlcyan{$\LTwoSpace[F]$-orthogonal} polynomials on $F$ of degree~$n$.

@@

	Integrating \eqref{lambda_intermsof_moments} over all mini-faces $f \in \mfaces_\bface(\bcell)$ ($f$ has local index $i$ among mini-faces belonging to $F$) and re-scaling, we get
	\begin{equation}\label{asc1_interp}
		\lambda_{j\,i}(\mmesh) =
		\begin{cases}
			\lambda^{(0)}_{j}(\bcell) +  s_{j\,i}\,\lambda^{(1)}_{j}(\bcell), & \text{if}~F~\text{is a multi-material face}, \\
			\lambda^{(0)}_{j}(\bcell),                                        & \text{otherwise},
		\end{cases}
	\end{equation}
	\hlcyan{where $s_{j\,i} \equiv s_f$ is a signed distance between centroids of~$f$  and~$F$, i.e. if $\vect a_F$, $\vect b_F$ and $\vect a_f$, $\vect b_f$ are vertices forming macro-face~$F$ and mini-face~$f$, respectively, then we have}
	\begin{equation}\label{sdist}
		s_f \coloneqq \left\| \frac{\vect a_f + \vect b_f}{2} - \vect a_F \right\|_2 - \left\| \frac{\vect a_F + \vect b_F}{2} - \vect a_F\right\|_2.
	\end{equation}

>>>>

\title{A higher order approximate static condensation method for multi-material diffusion problems}
\author{
	Alexander Zhiliakov\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (alex@math.uh.edu).}
	\and Daniil Svyatskiy\thanks{Los Alamos National Laboratory, Los Alamos,
		New Mexico, USA (dasvyat@lanl.gov).}
	\and
	Maxim Olshanskii\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 and Sechenov University, Moscow  (molshan@math.uh.edu); Partially supported by NSF through grant  DMS-1717516.}
	\and Evgeny Kikinzon \thanks{Los Alamos National Laboratory, Los Alamos,
		New Mexico, USA (kikinzon@lanl.gov).}
	\and Mikhail Shashkov\thanks{Los Alamos National Laboratory, Los Alamos,
		New Mexico, USA (shashkov@lanl.gov).}
}

@@

	Past decades evidenced an explosive {\color{blue}growth in the development of efficient computational techniques} for problems with evolving interfaces, which involve interaction between many materials or different phases of matter. These developments include immersed boundary method~\cite{peskin2002immersed}, immersed interface method~\cite{leveque1994immersed}, and unfitted finite element methods \cite{belytschko2009review,burman2015cutfem}, to name several popular numerical approaches. Depending on how the interface is treated numerically, one can distinguish between methods that smear the interface over a strip of finite thickness which should be further resolved by the mesh, like in the phase field approach~\cite{steinbach2009phase}, and methods that use a sharp interface representation, as in the level-set method \cite{sethian1999level}.  If one applies a sharp representation to handle complex geometries or interfaces undergoing large deformations, it is convenient to allow the  interface to cut through the background mesh in an arbitrary way. In turn, this leads to the problem of building accurate and stable approximations for  so-called multi-material cells, i.e. the mesh cells intersected by material interfaces. In particular, one is interested in discretizations which are robust with respect to how interfaces intersect the mesh and with respect to the contrast of  material properties, e.g. the ratio of physical parameters. This is the setting and the problem  we focus in this paper.

@@

One standard approach to handle  multi-material cells is a homogenization procedure. In this approach, one assigns to the cells  artificial homogeneous  material properties, which are calculated based on the volumetric shares of different materials in each of the multi-material cells. This enables one to apply standard discretization {techniques}. %if one needs to solve for other physics, such as the heat transfer, on every time step of the simulation.
     %Then, ad-hoc methods can be used to interpolate the solution for the contained materials based on
Further one recovers solution in each phase from the computed cell-averaged values~\cite{dawes2013solving}.
Although being technologically straightforward, the homogenization approach often fails  to accurately model subcell material interactions, which results in non-physical numerical solutions to problems with high-contrast material properties.

@@

	Denote by $\bfaces$ the collection of all faces of the macro-mesh $\bmesh$. {\color{blue}We shall distinguish between the subset of internal and external faces},  $\bfaces = \bfaces[int] \cup \bfaces[ext]$\footnote{For the sake of  notation, we shall use~$\bfaces$ to denote both the set of elements and the corresponding domain formed by their union~$\cup_{F\in \bfaces} \bar{F}$; same for $\bfaces[int]$, $\bfaces[ext]$ and other collections of mesh elements introduced later in the text. The meaning should be clear from a context.}.
	Introducing the new unknown $\lambda \in \HHalfSpace[\bfaces]$, we reformulate \eqref{dual}--\eqref{dual:bc} as a system of local problems coupled through the boundary data
	and flux continuity condition:
	\begin{eqnarray}
		\arraycolsep=2pt\def\arraystretch{1.5}
		\left\{\begin{array}{rcrccl}
			\vect K^{-1}\,\vect u                    & + & \nabla\,p & = & 0       &\quad\text{in } \bcell, \\
			\nabla\cdot\vect u                       & + & c\,p      & = & f       &\quad\text{in } \bcell, \\
			                                         &   & p         & = & \lambda &\quad\text{on } \partial\bcell, %\label{dual_mini:trace}
		\end{array}\right.
		& \qquad \forall~\bcell\in\bmesh, \label{dual_mini} \\
		\llbracket\vect u \cdot \hat{\vect n}\rrbracket = 0\quad\:\:\text{on } F,\:\:\:\:
		& \qquad\quad \forall~F\in\bfaces[int]. \label{flux_cond}
	\end{eqnarray}
	Here $\hat{\vect n}$ denotes a normal vector to the face $F\in\bfaces[int]$ and $\llbracket \vect u\cdot\hat{\vect n} \rrbracket$ is the jump of the normal flux across $F$. On the outer boundary $\partial\Omega$ we assume \eqref{dual:bc}.

@@

	Consider an arbitrary but fixed cell $T\in\bmesh$. We now introduce the discretization of the local diffusion problem \eqref{dual_mini} in $T$. To this end, we consider the local mesh $\mmesh(T)$ of $T$, which is referred as mini-mesh. While the original triangulation $\bmesh$ is referred as macro-mesh.
	\begin{wrapfigure}{r}{0.4\textwidth}
		\vspace{-10pt}
		\begin{center}
			\includegraphics[width=0.3\textwidth]{./ring_mini_voronoi_cell.png}%{./Pictures/mainscreen1.png}
			\caption{Local polyhedral mesh for a three-material cell $T\in\bmesh$ \label{fig:mmesh}}
		\end{center}
		\vspace{-15pt}
		\vspace{1pt}
	\end{wrapfigure}
	If $T$ contains only one phase or material, then we obviously have $\mmesh(T) = \{\bcell\}$. Otherwise for the cell shared by several phases, $\mmesh(T)$ consists of polygonal elements, forming a tessellation of $T$, such that any ${\tau \in \mmesh(T)}$ contains only one phase/material; see Figure~\ref{fig:mmesh}. We denote by $\mfaces(T)$ the set of all faces in $\mmesh(T)$, which collects both   internal and boundary (external) faces with respect to $T$,  $\mfaces(T) = \mfaces[int](T) \cup \mfaces[ext](T)$. {\color{blue}If the meaning is not obvious from the context, we will refer to elements of~$\mfaces(T)$ as ``mini-faces," and to elements of~$\bfaces$ as ``macro-faces."} Thus for the example of local mesh drafted in Figure~\ref{fig:mmesh}, we have three elements in $\mmesh(T)$, two internal faces from $\mfaces[int](T)$ and eleven external faces from $\mfaces[ext](T)$. It is clear that this local mesh is fitted to the material interfaces.

@@

	Given the above definition of the degrees of freedom on the local mesh we apply the mimetic finite difference (MFD) method from~\cite{lipnikov2014mimetic}. The method leads to the following system of equations with the matrix having the block structure:
	\begin{equation}\label{local}
		\begin{pmatrix}
			\phantom{-}\vect M_\mmesh & \vect B^T_\mmesh \\
			-\vect B_\mmesh & \vect \Sigma_\mmesh
		\end{pmatrix}
		\begin{pmatrix}
			{\vect u}_\mmesh \\
			{\vect p}_\mmesh
		\end{pmatrix}
		=
		\begin{pmatrix}
			\vect E_\mmesh\,\vect C_\mmesh\,{\vect \lambda}_\mmesh \\
			{\vect f}_\mmesh
		\end{pmatrix}.
	\end{equation}
	Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively; {\color{blue}$-\vect C_\mmesh$ is a diagonal scaling matrix  with diagonal elements equal to the measures $|f|$ of mini-faces $f \in \mfaces[ext](T)$, i.e. $-\vect C_\mmesh$ is the mass matrix for ${\vect \lambda}_\mmesh$ unknowns};
	$\vect E_\mmesh \in \mathbb{R}^{n_f \times n_\lambda}$ is a rectangular matrix with 0 and 1 entries which sparsifies a vector from  $\mathbb{R}^{n_{\lambda}}$
	to a vector from  $\mathbb{R}^{n_{f}}$.
	For the details on MFD and accurate definition of the matrices we refer to \cite{lipnikov2014mimetic,MFDbook}.
	Here we need the property that  $\vect B_\mmesh$ has a full row rank, and $\vect M_\mmesh = \vect M^T_\mmesh$ is positive definite.

	Since the continuity of flux condition \eqref{flux_cond} and boundary conditions are enforced on  the \emph{external} edges of $T$, {\color{blue}we need to distinguish the vector} ${\vect u}^\text{ext}_\mmesh$ of fluxes on $\mfaces[ext](T)$, which is just a trivial restriction of ${\vect u}_\mmesh$ on the edges  from $\mfaces[ext](T)$,
	\begin{equation}\label{system_mini}
		{\vect u}^\text{ext}_\mmesh \coloneqq \vect E_\mmesh^T\,{\vect u}_\mmesh,
	\end{equation}
	where $\vect E_\mmesh^T$ is the restriction matrix with entries equal $0$ or $1$.

@@

	Next, we should use the continuity of flux condition \eqref{flux_cond} and boundary conditions to obtain a complete system for ${\vect u}^\text{ext}_\mmesh$ and ${\vect \lambda}_\mmesh$. However, we cannot do this in a straightforward way, since the discontinuity of material interfaces across the macro-mesh faces may lead to a mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$. {\color{blue}We elaborate on this below.}

	{\color{blue}For $F \in \bfaces[int]$ shared by two polygonal cells~$\bcell^\pm\in \bmesh$ denote by~$\mfaces_F(T^\pm) \subset \mfaces_{\text{ext}}(T^\pm)$ the subsets of mini-faces that belong to the macro-face~$F$ from each side. In general, $\mfaces_F(T^+)$ and $\mfaces_F(T^-)$ may have a different number of mini-faces that make up the macro-face~$F$, i.e. $\#\,\mfaces_F(T^+) \ne \#\,\mfaces_F(T^-)$, and hence the restrictions of concentration vectors~${\vect \lambda}_\mmesh$ and fluxes vectors~${\vect u}^\text{ext}_\mmesh$ can be of different sizes. Even if~$\#\,\mfaces_F(T^+) = \#\,\mfaces_F(T^-)$, the locations of the mini-faces may be different due to volume- or moment-of-fluid interface reconstruction.}
	\begin{wrapfigure}{l}{0.5\linewidth}
		\begin{subfigure}{1\linewidth}
			\svginputw{e_plus_e_minus.pdf_tex}
		\end{subfigure}%
%		\quad
%		\begin{subfigure}{.49\linewidth}
%			
%		\end{subfigure}
		\caption{{\color{blue}Example of the mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$}}
		\label{fig:mismatch}
	\end{wrapfigure}
{\color{blue}See an example in Figure~\ref{fig:mismatch}. We have $3 = \#\,\mfaces_F(T^+) \ne \#\,\mfaces_F(T^-) = 2$. Note also that locations of mini-faces corresponding to the same material are different from each side of~$F$}.	
	{\color{blue}This makes matching concentration and fluxes values not straightforward.} Therefore, we shall enforce the flux continuity condition in the spirit of the mortar finite element method~\cite{mortar} using the space of functions defined on $\bfaces[int]$, which are polynomials of degree at most $n$ on every $F\in\bfaces[int]$, an analog of the Lagrange multiplier space in the mortar method:
	\[
		\Lambda=\left\{\lambda\in \LTwoSpace[{\bfaces[int]}]\,:\, \lambda\in P_n~\text{for any}~F\in\bfaces[int]\right\}.
	\]

	When the Lagrange multiplier space $\Lambda$ couples local MFD solutions, it is convenient to define
	degrees of freedom for $\lambda\in\Lambda$ in terms of its~$(n+1)$ moments $\lambda^{(i)}_F$ on every internal face $F\in\bfaces[int]$:
	\begin{equation}\label{asc_dofs}
		\lambda^{(i)}_F=\frac{\int_F  \lambda\,s_i \diff l}{|F|}, \quad i = 0, \dots, n.
	\end{equation}
	Here~$\{\,s_i\,\}_{i=0,\dots,n}$ is the set of {\color{blue}$\LTwoSpace[F]$-orthogonal} polynomials on $F$ of degree~$n$.

@@

	Integrating \eqref{lambda_intermsof_moments} over all mini-faces $f \in \mfaces_\bface(\bcell)$ ($f$ has local index $i$ among mini-faces belonging to $F$) and re-scaling, we get
	\begin{equation}\label{asc1_interp}
		\lambda_{j\,i}(\mmesh) =
		\begin{cases}
			\lambda^{(0)}_{j}(\bcell) +  s_{j\,i}\,\lambda^{(1)}_{j}(\bcell), & \text{if}~F~\text{is a multi-material face}, \\
			\lambda^{(0)}_{j}(\bcell),                                        & \text{otherwise},
		\end{cases}
	\end{equation}
	{\color{blue}where $s_{j\,i} \equiv s_f$ is a signed distance between centroids of~$f$  and~$F$, i.e. if $\vect a_F$, $\vect b_F$ and $\vect a_f$, $\vect b_f$ are vertices forming macro-face~$F$ and mini-face~$f$, respectively, then we have}
	\begin{equation}\label{sdist}
		s_f \coloneqq \left\| \frac{\vect a_f + \vect b_f}{2} - \vect a_F \right\|_2 - \left\| \frac{\vect a_F + \vect b_F}{2} - \vect a_F\right\|_2.
	\end{equation}

	For the corresponding vectors of unknowns  ${\vect \lambda}_\mmesh = \{ \lambda_{j\,i}(\mmesh) \}$ and ${\vect \lambda}_\bcell = \{ \lambda^{(0)}_{j}(\bcell) \} \cup \{ \lambda^{(1)}_{j}(\bcell) \}$ equation \eqref{asc1_interp} defines
	the matrix $\vect R_\mmesh$ through~\eqref{asc_lambda}. For the example in Figure~\ref{fig:asc_dofs:asc1:mmc} (left and right) we have
	\begin{equation*}\footnotesize
		\vect R_\mmesh
		=
		\begin{pmatrix}
			1 &  s_{1\,1} & 0 & 0 & 0 & 0 & 0 \\
			1 &  s_{1\,2} & 0 & 0 & 0 & 0 & 0 \\
			1 &  s_{1\,3} & 0 & 0 & 0 & 0 & 0 \\
			0 & 0 & 1 &  s_{2\,1} & 0 & 0 & 0 \\
			0 & 0 & 1 &  s_{2\,2} & 0 & 0 & 0 \\
			0 & 0 & 1 &  s_{2\,3} & 0 & 0 & 0 \\
			0 & 0 & 0 & 0 & 1 &  s_{3\,1} & 0 \\
			0 & 0 & 0 & 0 & 1 &  s_{3\,2} & 0 \\
			0 & 0 & 0 & 0 & 0 & 0 & 1
		\end{pmatrix},
		\quad
		\vect \lambda_\mmesh =
		\begin{pmatrix}
			\lambda_{11}(\mmesh) \\
			\lambda_{12}(\mmesh) \\
			\lambda_{13}(\mmesh) \\
			\lambda_{21}(\mmesh) \\
			\lambda_{22}(\mmesh) \\
			\lambda_{23}(\mmesh) \\
			\lambda_{31}(\mmesh) \\
			\lambda_{32}(\mmesh) \\
			\lambda_{41}(\mmesh) \\
		\end{pmatrix};	
	\end{equation*}
	for the moment d.o.f. we have
	\begin{align*}\footnotesize
		\vect \lambda_\bcell =&
		\left(
			\lambda^{(0)}_1(\bcell),\,
			\lambda^{(1)}_1(\bcell),\,
			\lambda^{(0)}_2(\bcell),\,
			\lambda^{(1)}_2(\bcell),\,
			\lambda^{(0)}_3(\bcell),\,
			\lambda^{(1)}_3(\bcell),\,
			\lambda^{(0)}_4(\bcell)
		\right)^T
		\text{ and} \\
		&\left(
			\lambda^{(0)}_1(\bcell),\,
			\lambda^{(1)}_1(\bcell),\,
			\lambda^{(0)}_2(\bcell),\,
			\lambda^{(1)}_2(\bcell),\,
			\lambda^{(0)}_3(\bcell),\,
			\lambda^{(1)}_3(\bcell),\,
			\lambda^{(0)}_4(\bcell),\,
			\lambda^{(1)}_4(\bcell)
		\right)^T		
	\end{align*}
	for Figure~\ref{fig:asc_dofs:asc1:mmc} (left) and Figure~\ref{fig:asc_dofs:asc1:mmc} (right), respectively. For ASC(0) the matrix $\vect R_\mmesh$  is as above with rows containing $s_{ij}$-s eliminated.
	%Since the fourth base\,face $F \in \bfaces_\bcell$ has only one material, a trace on~$F$ from the cell~$\bcell$ is approximated by a constant. However, if in the adjacent cell we have several materials on $F$\footnotemark{}, we will use the value of~$\lambda'_{\bcell\,4}$ to improve the approximation of the fine traces on~$F$ in the adjacent cell.
